Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-01-28 text/src/article.tex
Draft section for conclusions

  * Do one thing and do it well
  * If your data structures are good enough, the algorithm to manipulate them should be trivial."

>>>>

Scaffolder follows the Unix philospophy ``Do one thing and do it well''.
Scaffolder focuses on creating a simple to use and install tool for generating
a genome scaffold. The YAML data format for creating a scaffold file is
standardised and easily manipulated programmatically. This thereby follows
a second Unix tenet: ``If your data structures are good enough, the algorithm
to manipulate them should be trivial.''
